\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Abhishek Sharma} \\[7.5pt]
\href{https://www.linkedin.com/in/asharma-97/}{\raisebox{-0.05\height}\faLinkedin\ asharma-97} \ $|$ \ 
\href{https://github.com/asharma-97}{\raisebox{-0.05\height}\faGithub\ asharma-97} \ $|$ \ 
\href{mailto:abhishekuchain@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ abhishekuchain@gmail.com} \ $|$ \ 
\href{tel:+917976554280}{\raisebox{-0.05\height}\faMobile \ +917976554280} \ $|$ \
\href{https://www.google.com/maps/place/Bengaluru,+Karnataka/@12.9542802,77.4661308,11z/}{\raisebox{-0.05\height}\faMapMarker \ Bangalore} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Seasoned backend engineer with expertise in micro-services architecture and solving challenging business problems with strong software design skills.

%Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Software development engineer 3 | Flipkart, Bengaluru} & \hfill Jul 2021 - present \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Working in \textbf{Flipkart retail} - managing the master data for products, listings and propagation of inventory from warehouse to end users.
        \item[--] \textbf{Lead a team of 10 engineers}, highly involved in tech, product \& domain level solutionings, tech staff sessions and hiring events.
        \item[--] Redesigned flipkart's \textbf{lot management system from scratch} on HBase and migrated 12 million SKU's with no downtime. Lead team of 4 engineers and fixed core business problems related to lot lifecycle management by taking bottom up initiatives.
        \item[--] Created an \textbf{async priority aware system} for \textbf{inventory ingestion flows} which promised TAT \textbf{under 5 mins} for hyperlocal inventory using apache pulsar.
        \item[--] \textbf{Designed distributed locking library} on zookeeper \& \textbf{camel's implementation with pulsar}
        \item[--] Planned out big migrations with different strategies like \textbf{paraller paths, phased migration} to avoid big bang changes in multiple places.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Software engineer | Oracle, Hyderabad} & \hfill Jun 2019 - Jul 2021 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Worked in \textbf{Oracle infinity} - a data collection and analytics product.
        \item[--] Using \textbf{functional + OOP design patterns} to write maintainable \& extensible code in scala with a good understanding of \textbf{microservice architecture}.
        \item[--] Created public APIs contracts and implemented on HTTP 2.0 for new MVP. Used \textbf{gRPCs proto buffs} for microservice communication which were significantly faster then http based communication.
        \item[--] Create \textbf{query parser service} which generates complex processing queries from user’s friendly input. \item[--] Optimised authorization logic which resulted in \textbf{90\% faster access} to the application.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

%Projects
\section{Projects}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
Waste Classifier based on CNNs & \hfill 2018 \\ 
Chatbot based on LSTMs under the guidance of dr. Divya Kumar. & \hfill  2019 \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2015 - 2019 & B.Tech (\textbf{CSE}) at \textbf{NIT, Allahabad} \hfill (GPA: 8.03) \\ 
2014 & Class 12th RBSE \hfill  (87.20) \\
2012 & Class 10th RBSE \hfill  (82.33) \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Java, Microservices, Dropwizard, Scala, Akka, Mysql, HBase, MongoDB, ElasticSearch, Zookeeper,\\ Kafka, RMQ, Apache Pulsar, Apache camel, CI/CD, Open API
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
